\section{Procedure}

This experiment was split into three parts:
Part I was the observation of the dissolution of solid \koh into an aqueous solution,
Part II was the observation of the dissolution of solid \koh into an aqueous \hcl solution,
and Part III was the observation of the solution produced in Part I being mixed with aqueous \hcl.

\subsection*{Part I}
A beaker was weighed, and then approximately two grams of solid \koh were weighed in the beaker. 
The mass of the \koh sample was recorded. 
The Microlab software was started on the lab computer and set up to record temperature over time using a thermistor. 
\SI{100.0}{mL} of deionized water was measured and placed into the styrofoam cup. 

The end of the thermistor was placed into the cup, with the tip held approximately a half-inch from the bottom and without contacting the walls of the cup. 
The temperature was recorded for approximately 120 seconds.  
Without removing the thermistor, the solid \koh was added to the styrofoam cup and stirred for approximately three minutes. 
The temperature was recorded for the duration of this process.

The solution was moved from the styrofoam cup to a glass beaker for later use. 
Data from the Microlab data recording tool was exported and saved. 

\subsection*{Part II}
A beaker was weighed, and then approximately two grams of solid \koh were weighed in the beaker. 
The mass of the \koh sample was recorded. 
The Microlab software was started on the lab computer and set up to record temperature over time using a thermistor, as done in Part I.

Approximately \SI{160}{mL} of 1.5 M \hcl was placed into a beaker.
 \SI{100.0}{mL} of this was then poured into the styrofoam cup.
For approximately two minutes, the temperature of the \hcl was recorded using the thermistor and Microlab.
The solid \koh measured out previously was added to the styrofoam cup and continuously stirred for about three minutes,
while continuing recording the temperature. Following this, a small amount of the solution was applied to a pH strip and the results recorded. 

The solution from the styrofoam cup was disposed, and the Microlab data exported and saved. 

\subsection*{Part III}

\SI{50.0}{mL} of the \koh solution from Part I was placed into a clean beaker. 
\SI{50.0}{mL} of the 1.5 M \hcl was placed into the styrofoam cup.
The thermistor was placed into the \koh beaker and the temperature recorded for about two minutes,
and the temperature data from this measurement exported and saved from Microlab.

The thermistor was then held in the styrofoam cup and temperature data of the \hcl was gathered for about two minutes in a new Microlab experiment file. 
The \SI{50.0}{mL} of \koh was added to the styrofoam cup and mixed for about three minutes, while the temperature was continually measured. 
After these three minutes, a small sample of the solution was applied to a pH strip and the results recorded. 
The solution was then disposed and the data exported and saved. 

